---
title: "Can Internet Regulation Prevent Fake News?"
author: "Dr Andrea De Angelis"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document
---

```{r setup, include=FALSE}

# This sets as default the inclusion of the R code from the report:
knitr::opts_chunk$set(echo = FALSE)

# Source setup scripts:
source(here::here("src","00_setup.R"))

# Eventually attach packages here:
library(stargazer)
library(tidyverse)
library(here)

# Load data:
load(here::here("output","DSP_recoded.Rdata"))
```

## Abstract
This is an example of an RMarkdown automated report.

# Descriptives
This report uses DSP data to investigate whether Internet regulation can prevent fake news. 
The DSP data contains `r nrow(DSP_rec)` observations from year 1980 until 2019.  

The `v2smregcon` variable measures the level of legal framework protection that the country adopted to regulate the Internet. This is the distribution of this variable:

```{r echo=FALSE}
ggplot(DSP_rec) + 
     geom_histogram(mapping = aes(x = v2smregcon)) + 
     labs(x = "", title = "Histogram of v2smregcon") + 
     theme_bw()
```

We hypothesize that better regulatory frameworks of the Internet can prevent the diffusion of fake news operated by government with the goal of propaganda. Variable `v2smgovdom` measures how often the government uses social media to disseminate false of misleading news to influence public opinion. 
We count `r sum(!is.na(DSP_rec$v2smgovdom))` non-missing values.   
The following histogram shows the distribution of the variable:

```{r echo=FALSE}
ggplot(DSP_rec) + 
     geom_histogram(mapping = aes(x = v2smgovdom)) + 
     labs(x = "", title = "Histogram of v2smgovdom") + 
     theme_bw()
```

# Regression analysis

We thus estimate a linear regression model to test our hypothesis that greater regulatory framework reduces the amount of fake news. These are the results:

```{r echo=FALSE, results='asis'}
# resuls='asis' explained here: https://stackoverflow.com/questions/14670299/using-stargazer-with-rstudio-and-knitr

# Model 1: baseline specification
fm_govdom1 <- lm(v2smgovdom ~ v2smregcon, data = DSP_rec)

# Model 2: adding country fixed-effects:
fm_govdom2 <- lm(v2smgovdom ~ v2smregcon + country_name, data = DSP_rec)

# Model 3: adding year fixed-effects
fm_govdom3 <- lm(v2smgovdom ~ v2smregcon + country_name + year, data = DSP_rec)

stargazer(fm_govdom1, fm_govdom2, fm_govdom3, 
          type = "html", style = "apsr",
          omit = c("country_name", "year"), 
          add.lines = list(c("Country FE", "No", "Yes", "Yes"), 
                           c("Year FE", "No", "No", "Yes")))
```

